Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-04-05 paper/paper.qmd
Minor changes

Instead, we refer to Cohen’s \(f\) as a more appropriate measure of effect size in ANOVA. Cohen’s \(f\) is based on the proportion of variance explained and provides context for the magnitude of the observed effects. [[[SHOULD WE STILL INCLUDE THIS?: For this study, we assume a medium effect size, corresponding to Cohen’s $f \approx 0.25$, based on conventional benchmarks from lecture materials. Even though the statistical test did not yield significant results. This suggests a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.]]]

We did a post-hoc power analysis using @WebPower. Based on the overall $\eta^2$ from the ANOVA model, we calculated a Cohen's f value of 0.204. This suggests a small-medium effect size, which means that the type of drug and dosage level may still have had a meaningful impact on memory task performance.

@@

>>>>

Instead, we refer to Cohen’s $f$ as a more appropriate measure of effect size in ANOVA. Cohen’s $f$ is based on the proportion of variance explained and provides context for the magnitude of the observed effects. [[[SHOULD WE STILL INCLUDE THIS?: For this study, we assume a medium effect size, corresponding to Cohen’s $f \approx 0.25$, based on conventional benchmarks from lecture materials. Even though the statistical test did not yield significant results. This suggests a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.]]]

We did a post-hoc power analysis. Based on the overall $\eta^2$ from the ANOVA model, we calculated a Cohen's $f$ value of 0.204. This suggests a small-medium effect size, which means that the type of drug and dosage level may still have had a meaningful impact on memory task performance.

@@

library(tidyverse)
library(janitor)
library(here)
library(lubridate)
library(patchwork)
library(arrow)
library(effectsize)
library(dplyr)
library(knitr)
library(performance)
library(modelsummary)
library(kableExtra)
library(performance)
library(WebPower)
library(ggpubr)
